Individual heterogeneity in the functional network topography of medial prefrontal cortex

### 2019-05-26 Manuscript.Rmd
done! ready for preprinting.

# general options
threshMaps <- TRUE # Whether to apply subject-wise thresholds on maps or not
permute <- FALSE # show meta-analysis permutation progress? (SLOW)

@@

# optional because it can take a long time to run
if (permute) {

@@

Figure 7B shows the test/re-test reliability across days for patterns derived using community detection, seed-based correlation, and across methods (e.g. Day 1 community detection versus Day 2 seed-based correlation). While both approaches were reliable, community detection displayed a significantly higher mean correlation coefficient across days than seed-based correlation (Community: mean = `r round(mean(tempComm), digits = 2)`, SD = `r round(sd(tempComm), digits = 2)`; Seed-based: mean = `r round(mean(tempCor), digits = 2)`, SD = `r round(sd(tempCor), digits = 2)`; paired permutation *p* `r ifelse(prepostComp_permTest$Pval < 0.001, "< 0.001", paste("=", prepostComp_permTest$Pval))`; Cohen's D = `r round(prepostComp_ES, digits = 2)`). Agreement across methods was fair (mean = `r round(mean(tempBoth), digits = 2)`, SD = `r round(sd(tempBoth), digits = 2)`), signifying that the two approaches identified similar topographic features but also had systematic differences. These findings suggest that graph-theoretic community detection algorithms are advantageous for detecting stable functional topologies, in addition to their other advantages of being data-driven, unbiased and observer agnostic.

>>>>

# general options
threshMaps <- TRUE # Whether to apply subject-wise thresholds on maps or not
Permute <- FALSE # show meta-analysis permutation progress? (SLOW)

@@

# optional because it can take a long time to run
if (Permute) {

@@

Figure 7B shows the test/re-test reliability across days for patterns derived using community detection, seed-based correlation, and across methods (e.g. Day 1 community detection versus Day 2 seed-based correlation). While both approaches were reliable, community detection displayed a significantly higher mean correlation coefficient across days than seed-based correlation (Community: mean = `r round(mean(tempComm), digits = 2)`, SD = `r round(sd(tempComm), digits = 2)`; Seed-based: mean = `r round(mean(tempCor), digits = 2)`, SD = `r round(sd(tempCor), digits = 2)`; paired permutation *p* `r ifelse(prepostComp_permTest$Pval < 0.001, "< 0.001", paste("=", round(prepostComp_permTest$Pval, digits = 3)))`; Cohen's D = `r round(prepostComp_ES, digits = 2)`). Agreement across methods was fair (mean = `r round(mean(tempBoth), digits = 2)`, SD = `r round(sd(tempBoth), digits = 2)`), signifying that the two approaches identified similar topographic features but also had systematic differences. These findings suggest that graph-theoretic community detection algorithms are advantageous for detecting stable functional topologies, in addition to their other advantages of being data-driven, unbiased and observer agnostic.
